Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-27 concepts.tex
fixed notes on dependency

The aim of a Design Space Exploration (DSE) strategy is to give a
good approximation of the Pareto-optimal set for a system $S$ and an
application $b$, simulating as few configurations as possible.

%----------------------------------------------------------------

As we will show later, at each iteration, PS calculates an approximation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on. The image of $\mathscr{P}_i$ is an approximation of the Pareto-front.
The simulation effort is distributed more on the regions that provide configurations in $\mathscr{P}_i$ which introduce more \emph{innovation}, i.e. whose image in the objective space is more distant, thus ``more different'', from the previous Pareto-front approximation point.

>>>>

Another fundamental concept, which adds further complexity to the
problem of multiobjective design space exploration, is the following

\begin{definition}[Parameter dependencies]
\defL{dependency}
Given a system $S$, application $b \in \mathcal{B}$ and two parameters
$p_x$ and $p_y$, $p_x$ is said to
be dependent on another parameter $p_y$ if the optimal value of $p_x$,
that is the $v_{x} \in V_x$ which optimizes the objectives of the
evaluation function $E$, is dependent upon the current value of $p_y$. 
\end{definition}

When a dependency is present any safe assumption about the ``meaning'' of
$p_x$ in order to intuitively choose an appropriate value that
optimizes objective could be misleading.  It should be also pointed
out that it's often very difficult to identify dependencies using
analytical techniques and often designers have to use different
strategies to deal with such complexity, as seen
in~\secR{Related-work}.

The aim of a Design Space Exploration (DSE) strategy is to give a
good approximation of the Pareto-optimal set for a system $S$ and an
application $b$, simulating as few configurations as possible.
As we will show later, at each iteration, PS calculates an approximation $\mathscr{P}_i$ of the Pareto-set that approaches it as iterations go on. The image of $\mathscr{P}_i$ is an approximation of the Pareto-front.
The simulation effort is distributed more on the regions that provide configurations in $\mathscr{P}_i$ which introduce more \emph{innovation}, i.e. whose image in the objective space is more distant, thus ``more different'', from the previous Pareto-front approximation point.
